N-Body problem

### 2014-10-25 article/article.tex
softening voor lengte tussen bodies, geen dynamic timestep voor leapfrog

This lowering of the timestep is done globally, for the entire simulation. The simulation is slowed down based on the closest interaction between two bodies in the system. There are algorithms that lower the timestep per body, but those have not been looked at.

>>>>

This lowering of the timestep is done globally, for the entire simulation. The simulation is slowed down based on the closest interaction between two bodies in the system. There are algorithms that lower the timestep per body, but those have not been looked at.\\
The Euler and Jerk integrators can run in a optional dynamic timestep mode. The leapfrog because of its interleaving nature cannot legitimately be run in a dynamic timestep mode in the version implemented and has thus only been run in a fixed timestep mode.\\
Additionally a softening factor has been added to the calculations of forces between two object. The calculation for acceleration (and jerk) divides by a power of the distance between two bodies, which means that if the distance gets close to zero the force gets multiplied by a very big number. To soften this and make sure that (as far as the force calculations go) can't get infinitely close a small $\epsilon$ is added to the distance between two bodies in these calculations.
